Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-29 neurips-20/cvx-flats.tex
Citing Hari's paper

	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.
	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
	We particularly have $p \in F$ by construction.

@@

Let us verify the three conditions:
(i) $p\in\Gamma_r$ by construction.
(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W \cap \affhull(\simplex)$ for $W = [v]\in\reals^{1\times n}$.
Note that $\Gamma_r \subseteq F$, and \raf{$W$ does not contain the $\ones$ direction}, as the $y$ values are distinct by assumption.
As $p\in F$, Lemma~\ref{lem:affhull-relint} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 1 = d$.
(iii)
For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise $n\geq 3$.
\raft{I think we should punt this next bit to the appendix; it's pretty straightforward once you see what's happening, but really detracts from the simplicity of this example}
If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
Letting $W' = [v;v']\in\reals^{2\times n}$ where $v'_y = y^2-r^2-c$, and $F' = \ker W' \cap \affhull(\simplex)$, this would imply $\Gamma_r = F'\cap\simplex$ as well.
Lemma~\ref{lem:affhull-relint} applies again to show $F' = \affhull(\Gamma_r) = F$.
Yet as the $y$ values are distinct, $\rank(W')=2$ (for any $\alpha\in\reals$ there are at most two solutions to $y-r = \alpha(y^2-r^2-c)$), contradicting $\codim(F) = 1$.
Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.

>>>>

	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, we then have that each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
	With $W' := [W;\ones^T]$, we can now take $F := \ker(W') = \{x \in \affhull(\simplex) : W' x = \vec 0\}$, whose codimension is at most $d + 1$.
	We particularly have $p \in F$ by construction.

@@

Let us verify the three conditions:
(i) $p\in\Gamma_r$ by construction.
(ii) Letting $v\in\reals^\Y$ with $v_y = y - r$, define $F = \ker W$ for $W = [v;\ones]$.
Note that $\rank(W) = 2$, as the $y$ values are distinct by assumption.
From the second row of $W$ we have $F\subseteq\affhull(\simplex)$, so Lemma~\ref{lem:affhull-interior} gives $\affhull(\Gamma_r) = F$ and thus $\codim(\affhull(\Gamma_r)) = \rank(W) = 2 = d+1$.
(iii)
For $n \leq 2 = d+1$, $\Gamma_r=\{p\}$ is a singleton and we are done; otherwise, assume $n\geq 3$.
If $\Var[Y]$ were constant in $\Gamma_r$, then we would have some $c\in\reals$ such that $c = \Var_{p'}[Y] = \E_{p'} [Y^2] - r^2$ for all $p'\in\Gamma_r$.
Letting $W' = [v;v';\ones]$ where $v'_y = y^2-r^2-c$, by the same logic above we have $\ker W = \affhull(\Gamma_r) = \ker W'$, which contradicts $\rank(W)=2$.
Thus $\Var[Y]$ cannot be constant on $\Gamma_r$.
